 
\documentclass[margin,10pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\begin{document}
%\addtolength{\topmargin}{-.5in}
\name{Jaiden Gerig} % the \\[11	pt] adds a blank line after name

\address{{\bf Contact Information}\\ Phone: (512)-893-9148\\Email: jaideng123@yahoo.com \\}
\address{ {\bf Current Address} \\ 2708 Garden Springs Dr \\ Richardson, TX 75082 \\
       }

\begin{resume}
\section{}
\hspace*{-1.2in}Versatile Full-Stack Software Engineer specializing in
Front-End technologies, with experience building \\ \hspace*{-0.2in} web applications for
both small businesses and Fortune 100 companies

 
\section{EDUCATION}  {\bf B.S. Computer Science} Graduated: May, 2017  \\
                Texas A\&M University, College Station, TX
 
 
\section{WORK EXPERIENCE}   
				{\bf Capital One Financial - Plano, TX} \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                Associate Software Engineer &   June 2017 - Present
                \end{ncolumn}
                \begin{itemize}           
                \item \textit{Project Rebel (Loan Decisioning Tool)} - Partnered with UX designer to create indicators for high-risk auto deals and re-design our credit report display, Reduced run-time of front-end unit test suite from 10 minutes to 45 seconds. 
                \item \textit{Capital One Auto Pre-Approval Website} - Rebuilt front-end in Angular, led an integration with our Auto-Navigator website, and implemented new features such as a listener for failed email delivery, A/B testing, and usability surveys.
                \item \textit{Home Loans Origination Data Team} - Built a prototype with Angular and Go for a tool to help business analysts track the lineage and properties of data in Capital One's new data platform.
                \item \textit{Involvement} - As part of the Technology Development Program, I mentored interns and interviewed applicants to the program.
                \end{itemize}
				{\bf FrogSlayer Consulting LLC - Bryan, TX} \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                Junior Software Engineer &   Oct 2015 - Apr 2017
                \end{ncolumn}
                \begin{itemize}           
                \item \textit{Credit Insurance Reporting System} - Built new features in nodejs back-end, created a reusable OCR micro-service, met with client (a financial company), and managed the deployment of the entire system on AWS, all as the sole developer.
                \item \textit{Dog Registration Web Portal} - Worked with a small team to build an application for a nationally recognized Kennel Club, developed in AngularJS and .Net MVC.
                \end{itemize}
				{\bf Texas A\&M Computer Science Dept - College Station, TX} \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                Peer Teacher &   Aug 2014 - Dec 2016 
                \end{ncolumn}
                \begin{itemize}           
                \item[] Mentored students taking various CS courses
                \end{itemize}
 

                    
\section{TECHNICAL SKILLS}	
							\begin{itemize}
                    		\item[] 
\begin{tabular}{ll}
\textbf{\large Languages}  & \textbf{\large Technologies}        \\
\textbf{Javascript} Angular, React, Nodejs  & \textbf{Amazon Web Services} \\
\textbf{Java} Spring Boot   & \textbf{SQL Databases}       \\
\textbf{Python} Mostly for scripts  & \textbf{Kafka}               \\
\textbf{C\#} .NET MVC     & \textbf{Redis}               \\
\textbf{Go}        &                     \\
\textbf{Ruby}  Rails     &                     \\
\textbf{C++}        &                    
\end{tabular}
                    		\end{itemize} 
\section{OTHER PROJECTS}
				\begin{itemize}           
                	\item \textbf{TRITIX} - A mobile game I built and designed with Unity. Currently available on the Google Play Store.
                	\item \textbf{Prettier} - Open-source code formatting tool that I have made contributions to mainly fixing issues with the stability of comment formatting
                	\item[] \textbf{Github account:} https://github.com/jaideng123
                \end{itemize}
\end{resume} 
\end{document}





