 
\documentclass[resmargin,10pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue]{hyperref}
\topmargin=-0.5in
\usepackage[margin=0.5in, right=2.2in, left=.8in, top=.6in]{geometry}
\begin{document}
%\addtolength{\topmargin}{-.5in}
\name{\LARGE Jaiden Gerig} % the \\[11	pt] adds a blank line after name

\address{ \hspace*{0.8in} (512) 893-9148 $|$ jaideng123@yahoo.com $|$ 18549 Stone Ave N, Shoreline, WA 98133 \\
  \rule{\textwidth}{0.1pt}
  \\ \hspace*{1.5in}
\textbf{Games Portfolio:} \href{https://jaideng123.github.io/games/}{https://jaideng123.github.io/games/} \\}

\begin{resume}

\section{SUMMARY}
%\hspace*{-\sectionwidth}
Software engineer with multiple years experience building web applications and games.
 
\section{WORK EXPERIENCE}   
				{\bf Amazon.com} - Seattle, WA \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                Software Development Engineer II &  \hfill November 2020 - Present
                \end{ncolumn}
                                \begin{itemize}
                \item \textit{FC Games} - Build and improve games designed to motivate and engage associates at Amazon Fulfillment Centers. Major contributions include designing and building a new tutorial system to on-board players and a system for large-scale player contests.
                \end{itemize}
                                \begin{ncolumn}{2} % produces two equally spaced columns
                Software Development Engineer I &  \hfill March 2019 - November 2020
                \end{ncolumn}
                \begin{itemize}
                \item \textit{Inbound Automation} - Led project to create a new tool for associates at Amazon Fulfillment Centers to quickly stow pallets of items. Improved on-boarding resources and provided mentoring for new team members and interns.
                \end{itemize}
				{\bf Capital One Financial} - Plano, TX \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                Associate Software Engineer &  \hfill June 2017 - March 2019
                \end{ncolumn}
                \begin{itemize}           
                \item Developed front-end UI of multiple key products for Capital One's Auto-Finance division such as their \textit{Pre-Approval Website} and \textit{Loan Decisioning Tool}.
                \item Mentored interns and interviewed applicants for college-hire program.
                \end{itemize}
				{\bf FrogSlayer Consulting LLC} - Bryan, TX \\ 
                \begin{ncolumn}{2} % produces two equally spaced columns
                Junior Software Engineer &  \hfill Oct 2015 - Apr 2017
                \end{ncolumn}
                \begin{itemize}           
                \item  Built various web applications for small to mid-size businesses such as a \textit{Dog Registration Web Portal} and \textit{Credit Insurance Reporting System}.
                \item Met with clients to update progress and gather requirements, developed features using web technologies, and managed deployment \& hosting on AWS.
                \end{itemize}
                    
\section{TECHNICAL SKILLS}	
							\begin{itemize}
                    		\item[] 
\textbf{\large Languages}  \hspace*{.5in} \textbf{\large Technologies}        \\
\begin{tabular}{ll}
\textbf{C\#} \hspace*{1in}  & \textbf{Unity} \\
\textbf{Java} & \textbf{Amazon Web Services} \\
\textbf{C++}   & \textbf{OpenGL}       \\
\textbf{Python}  & \textbf{Git/GitHub}               \\
\textbf{Javascript} & \textbf{ImGui}               \\
\end{tabular}
                    		\end{itemize} 
\section{PERSONAL PROJECTS}
				\begin{itemize}       
				\item \textbf{ArrowBall} - Multiplayer arrow-sports game independently designed and built with Unity over a year-long development cycle. Available on Steam.
				                	\item \textbf{Where's My Keys?} - Submission for Global Game Jam created in collaboration with a team of artists, a sound designer, and another engineer. Featured on the official Unity Global Game Jam stream and TheGamer.com.
				                	                	\item \textbf{Rebound} - Submission for the Seattle Indies Slow Jam created with a team of artists, a sound designer, and myself as the sole engineer and gameplay designer. \\ Winner: Judges Choice \& Community Choice.
                	\item \textbf{TRITIX} - Turn-based mobile game independently built with Unity featuring both local and online multiplayer and AI opponents. Available on Google Play.
                	\item \textbf{Scratch-3D} - Rendering engine independently created with C++ and OpenGL. Features a scene editor with full serialization and deserialization and support for materials with custom shader properties. Supports Windows and Linux.
                \end{itemize}
                
\section{EDUCATION}
{\bf Texas A\&M University} - College Station, TX \hfill
Graduated: May 2017 \\
B.S. Computer Science,
\textit{Minor in Mathematics}
\end{resume} 
\end{document}





